Deeply Virtual Compton Scattering measurement off bound proton

### 2018-07-09 eg6-letters/incoherent/incoherent_prl.tex
Implement the last corrections from stepan

Electromagnetic probes have played a major role in advancing our knowledge 
about the structure of the nucleon. While lepton-nucleon elastic scattering 
measurements have 
taught us about the spatial charge and magnetization distributions 
\cite{Hofstadter:1955ae,Perdrisat:2006hj}, deep-inelastic scattering 
experiments have uncovered the partonic structure of the nucleon and 
the longitudinal momentum distributions of the 
constituents partons, i.e., quarks and gluons \cite{pdg}.  
With nuclear targets, deeply inelastic lepton scattering measurements 
have revealed the fact that the 
distribution of quarks in a nucleus is not a simple convolution of 
their distributions within nucleons, an observation known as the ``EMC 
effect''\cite{EMC_first} (for reviews on the topic, see  
\cite{Arneodo:1992wf,Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}).

@@

In the 
Bjorken regime, i.e, large virtual photon four-momentum squared 
($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant momentum transfer ($t=(p-p^\prime)^2$), the 
DVCS scattering process can be factorized, leaving the non-perturbative structure 
of the nucleon to be parametrized in terms of four chirally-even GPDs: $H$, 
$E$, $\widetilde{H}$, and $\widetilde{E}$, representing the four helicity-spin 
combinations of the quark-nucleon states \cite{Freund_Collins,Ji_Osborne}.

@@

In this Letter, we present the first exclusive measurement of the beam-spin 
asymmetry (BSA) in deeply virtual electroproduction of a real photon off a bound 
proton in $^{4}$He. FIG.~\ref{fig:diags} illustrates the 
leading-twist handbag diagram for this process. Experimentally, we measure the squared sum of the 
Bethe-Heitler (BH) and the DVCS amplitudes. The BH process, 
where the real photon is emitted by the incident or the scattered electron 
rather than the nucleon, dominates the cross section at our kinematics. The BSA arises from the interference 
of these two terms and is directly sensitive to the DVCS amplitude that contain 
the information on the GPDs. Using a longitudinally polarized electron beam 
(L) and an unpolarized target (U), the BSA is defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.

@@

%background
The two main backgrounds that contribute to the event sample after the exclusivity cuts are  
due to accidental coincidences and exclusive $\pi^0$ production where one of the photons 
from the $\pi^0$ decay escapes the detection. The contribution from accidental 
events, i.e., $e'p'\gamma$ collections 
with particles originating from different electron scatterings,
was evaluated to be of 6.5\% by selecting events passing all our selection cuts but originating from 
different vertices. The $\pi^0$ contamination was estimated using detector simulation and experimental 
data. From simulation, we calculated the ratio ($R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) 
of the number of $\pi^0$ 
events that are wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the 
number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$. Then 
in each kinematical bin and for 
each beam-helicity state, the $\pi^0$-subtracted experimental DVCS events is 
calculated as $N = N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow 
e'p'\pi^0}_{exp}$, where $N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is the 
number of $ep\rightarrow e'p'\gamma$ ($ep\rightarrow e'p'\pi^0$) experimentally identified. Depending on the 
kinematics, we found this contamination to be of 8 to 10\%.

@@

>>>>

Electromagnetic probes have played a major role in advancing our knowledge 
about the structure of the nucleon. While lepton-nucleon elastic scattering 
measurements have 
taught us about the spatial charge and magnetization distributions 
\cite{Hofstadter:1955ae,Perdrisat:2006hj}, deep-inelastic scattering 
experiments have uncovered the partonic structure of the nucleon and 
the longitudinal momentum distributions of the constituent partons, i.e., 
quarks and gluons \cite{pdg}.  With nuclear targets, deeply inelastic lepton 
scattering measurements have revealed the fact that the distribution of quarks 
in a nucleus is not a simple convolution of their distributions within 
nucleons, an observation known as the ``EMC effect''\cite{EMC_first} (for 
reviews on the topic, see  
\cite{Arneodo:1992wf,Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}).

@@

@@

In this Letter, we present the first exclusive measurement of the beam-spin 
asymmetry (BSA) in deeply virtual electroproduction of a real photon off a bound 
proton in $^{4}$He. FIG.~\ref{fig:diags} illustrates the leading-twist handbag 
diagram for this process. In the Bjorken regime, i.e, large virtual photon 
four-momentum squared ($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant 
momentum transfer ($t=(p-p^\prime)^2$), the DVCS scattering process can be 
factorized, leaving the non-perturbative structure of the nucleon to be 
parametrized in terms of four chirally-even GPDs: $H$, $E$, $\widetilde{H}$, 
and $\widetilde{E}$, representing the four helicity-spin combinations of the 
quark-nucleon states \cite{Freund_Collins,Ji_Osborne}. Experimentally, we 
measure the squared sum of the Bethe-Heitler (BH) and the DVCS amplitudes. The 
BH process, where the real photon is emitted by the incident or the scattered 
electron rather than the nucleon, dominates the cross section at our 
kinematics. The BSA arises from the interference of these two terms and is 
directly sensitive to the DVCS amplitude that contain the information on the 
GPDs. Using a longitudinally polarized electron beam (L) and an unpolarized 
target (U), the BSA is defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.

@@

%background
The two main backgrounds that contribute to the event sample after the exclusivity cuts are  
due to accidental coincidences and exclusive $\pi^0$ production where one of the photons 
from the $\pi^0$ decay escapes the detection. The contribution from accidental 
events, i.e., $e'p'\gamma$ collections 
with particles originating from different electron scatterings,
was evaluated to be of 6.5\% by selecting events passing all our selection cuts but originating from 
different vertices. The $\pi^0$ contamination was estimated using detector 
simulation and experimental data. From simulation, we calculated the ratio ($R 
= N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that 
are wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the 
number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$.  
Then in each kinematical bin and for each beam-helicity state, the 
$\pi^0$-subtracted experimental DVCS events is calculated as $N = 
N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
$N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is 
the number of the experimentally identified $ep\rightarrow e'p'\gamma$ 
($ep\rightarrow e'p'\pi^0$). Depending on the kinematics, we found this 
contamination to be of 8 to 10\%.

@@

\bibitem{Hattawy:thesis}
M.~Hattawy, Ph.D. thesis, Universit{\'e} Paris Sud - Paris XI, France, 2015 
[Institution Report No. 2015PA112161].
